\addcontentsline{toc}{chapter}{Preface \& Acknowledgements}
\chapter*{Preface \& Acknowledgements}

During the period of September to November 2006 I have been working at the
\ac{CADIA} research lab of the School of Science and Engineering of \ac{RU} in
Iceland.

I would like to thank Kristinn Thorisson of \ac{RU} for giving me this
opportunity and the useful input during the discussions we had before and
during the project.

The internship was supervised from the \ac{TU/e} by Huub van de Wetering, who
gave me useful hints and tips throughout the design and documentation phase and
I would like to thank for that.

When I considered doing part of my studies abroad, there was no agreeement with
any Icelandic institution yet. I had thought of an internship at a Scandinavian
university and by coincidence I discovered that - just weeks before - an
agreement was signed between \ac{TU/e} and \ac{RU}. 

From this position I would therefore also like to thank Jan-Friso Groote
(\ac{TU/e}) and Luca Aceto (\ac{RU}) for initiating this agreement.

Others who made my stay more pleasant were the people from the International
Offices of both \ac{RU} and the University of Iceland, my fellow students both
at \ac{CADIA} and the Erasmus Intensive Language Course in August and everybody
else I met during this period.

I have never experienced anything like this before. It was a unique experience
which I was happy to share with you all.

\vspace{2em}

Thank you all very much! Takk fyrir!

\Rvk{}, November 2006 \\
Christian Luijten
