\chapter{\label{cpt:requirements}Requirements}

There are various kinds of requirements to be identified. A distinction can be
made between functional and extra-functional (or non-functional) requirements.

\section{Extra-functional requirements}

\begin{enumerate}
  \item The system must make use of the Psyclone framework for communication.
  \item The system will be implemented in the Java programming language.
  \item The display module with the Java Applet must be able to run on any
    machine with a properly installed and recent Java Virtual Machine (i.e.
    not only on the machine running the rest of the system).
  \item It must be possible to add modules with similar functionality to
    operate in parallel with modules already there. For example when the Java
    Applet is running, it should also be possible to have the full screen
    module running at the same time. 
\end{enumerate}

\section{Functional requirements}

These requirements describe which \emph{inputs}, \emph{outputs}, \emph{storage}
and \emph{computations} exist in the system and how they are \emph{timed and
synchronized}. Finally, since this is a very important part of the project,
there are two separate sections on \emph{story analysis} and
\emph{visualization} requirements.

\subsection{Inputs}

\begin{enumerate}
  \item The system must be configurable to specify which sources will be
        monitored.
  \item The system will use the configuration to get information from the
        internet from the specified sources.
  \item Configuration of the system goes via Psyclone using module parameters.
  % \item The display may have a set of controls to navigate through the
  % history of a feed.
  \item Parts of the system must accept triggers from Psyclone whiteboards.
  \item Sources must be \ac{RSS} feeds, possibly aggregated via an \ac{OPML}
    file. The system should however be prepared to support other source types
    as well (i.e. it should be easily expandable).
  \item The Applet display is non-interactive (no input).
\end{enumerate}

\subsection{Outputs}

\begin{enumerate}
  \item There is an output module which is to be used within a website,
        i.e. a Java Applet.
  \item There is an output module which runs standalone and in full screen
        and displays more information than the Applet can.
\end{enumerate}

\subsection{Storage}

\begin{enumerate}
  \item The system on itself does not store anything.
\end{enumerate}

\subsection{Computations}

\begin{enumerate}
  \item The system must decide of a delivered story what its subject(s) is/are.
  \item The system may put weights on the subjects instead of a boolean value.
\end{enumerate}

\subsection{Timing and synchronization}

Synchronization between modules is handled by Psyclone, so no requirements need
to be added to the system itself.

\subsection{Story analysis}

\begin{enumerate}
  \item When stories come in, they are analysed by analysis modules.
  \item Every module adds some meta-information to the story depending on the
    module analysis.
\end{enumerate}

\subsection{Visualization}

The following requirements are common for both the applet and the standalone
viewer.

\begin{enumerate}
  \item A story is represented as a dot.
  \item In the center of the display is Earth (with picture?).
  \item Dots are launched into orbit around Earth.
  \item The dots leave fading trails as they move.
  \item There are some small, heavy bodies in ``geostationary'' orbit around
    Earth representing values of an enumeration of meta-information (for
    instance story subjects). They attract the stories depending on how much
    they match the story's subject. 
\end{enumerate}

There will be two different views, a static and a dynamic one. Which one is
used depends on the application. To get an idea of the activity at a certain
moment in time, the static view is used. For a ``real-time'' view of internet
activity, the dynamic view can be used.

The term ``static'' doesn't mean the image is standing still, it will behave
exactly the same as the dynamic view. However, some physical laws don't apply
or are differently calibrated in order to give a constant image. In other
words, while in dynamic view stories can appear and disappear, in the static
view the stories are a given constant.

\subsubsection{Differences between Applet and Standalone viewer}

\begin{enumerate}
  \item The applet display will in practice be considerably smaller than the
    standalone viewer. Therefore, the applet is less detailed and some physical
    laws might need to be bend a bit.
\end{enumerate}

