\chapter{\label{cpt:planning}Planning}

The actual internship period amounts to 14 weeks and starts week 34. Before the
actual working period has started, the assignment was already largely agreed
upon.

A week by week planning and logbook was held during the internship at the web
address \url{http://nemendur.ru.is/christian06/logbook.html}.

\section{Week 34 and 35}

\paragraph{Plan} Learning the organization, methodologies and procedures.

\paragraph{Actions} According to plan, read and talked a lot. Also experiments
with Psyclone.

\section{Week 36}

\paragraph{Plan} Having a global design of the modules and a first bit of
object model, meanwhile playing around with posting and retrieving messages
with Psyclone.

\paragraph{Actions} Mainly work on design, also created first version of the
Psyclone specification file.

\section{Week 37}

\paragraph{Plan} Finish global design, Think about visualization issues

\paragraph{Actions} Setting up project in Eclipse, preparing codebase. Laptop
got problems, installed a desktop computer. First simple prototype of
visualizer module (single dot orbiting a circle).

\section{Week 38}

\paragraph{Plan} Create detailed design, code along, starting with basic
visualization

\paragraph{Actions} Work on crawler design, problems with RSS architecture, no
thread support so initial ideas won't work.

\section{Week 39}

\paragraph{Plan} Create detailed design and code for crawler module. 

\paragraph{Actions} Almost completely finished crawler along with
documentation.

\section{Week 40}

\paragraph{Plan} Create detailed design and code for analysis modules.

\paragraph{Actions} Fully finished crawler, created simple analysis module.

\section{Week 41}

\paragraph{Plan} Continue detailed design and code for analysis modules.

\paragraph{Actions} Finished KeywordSpotter, enough data available to
visualize.

\section{Week 42}

\paragraph{Plan} Continue detailed design and code for visualization. By the
end of the week, the EarthView widget should be finished so that in the next
week the communication with Psyclone can be created.

\paragraph{Actions} First working visualization module, runs on own data
without psyclone.

\section{Week 43}

\paragraph{Plan} Continue detailed design and code for visualization. Enable
communication of visualizer with Psyclone. By the end of the week, the applet
should respond on new stories and incoming analyses.

\paragraph{Actions} Got visualizer working with Psyclone, particle trails
suggest clouds of interest, partly ported to OpenGL.

\section{Week 44}

\paragraph{Plan} Complete work at OpenGL visualization, return to crawler and
sieves to use parameter framework of Psyclone instead of own implementation.

\paragraph{Actions} Tried to implement texturing, failed to do so and reverted
back to old graphics. Modules are configured via parameters built in the
Psyclone system instead of by sending messages.

\section{Week 45}

\paragraph{Plan} Refactoring, fixing bugs, completing Javadoc code
documentation.

\paragraph{Actions} Preparing work for internship report document and source
code documentation for the design document. Implemented a way for the
visualization module to receive old data, in order to have a picture right from
the start.

\section{Week 46}

\paragraph{Plan} Fine-tune crawling, analysis and visualization parameters.
Create final distribution files. Test those on various platforms.

\paragraph{Actions} 

\section{Week 47}

\paragraph{Plan} Finish everything up. No more coding this week! Reserved for
``Goodbyes''.

\paragraph{Actions} 

\section{Week 48}

\paragraph{Plan} Finish internship report and paperworks.

\paragraph{Actions} 

