\chapter{\label{cpt:assignment}Assignment}

The original assignment as written down by Kristinn Thorisson:

\begin{quote}

  The ``Semantic Ambient Web Monitor'' project's goal is to give people a sense
  of online acitivity and community interest regarding particular topics of
  interest and discussion. The prototype will have a simple small area where
  elements related to online activity -- each dot representing e.g. a posting
  on an online forum or a blog site about the particular topic of interest.
  Each corner represent a concept related to the topic; If the topic to be
  monitored is ``artificial intelligence'', one corner might represent
  ``humanoid robots'', another might represent ``artificial neural networks'',
  a third could be ``expert systems'' and a fourth could be ``machine
  learning''. As the dots move they get pulled stronger towards the center the
  older they are; the more they relate to a concept the closer they get pulled
  towards the corner representing that concept.

  This produces very ``holistic'' patterns that can be interpreted in an
  instant by an onlooker: An equal distribution of dots would mean that all
  concepts are discussed equally, on average, in all postings. An oval orbit
  would mean that the majority of postings are about the concepts in oposite
  corners of the square, etc. If the dots left trails one could see how things
  change over time, e.g. days or months. Snapshots of the square, e.g. one per
  day or month, would give you a visual history of how the disucssion has
  changed over time regarding those concepts.

  The methodology that will be used to build the monitor enables a very
  incremental, modular approach. The software will be made open-source and thus
  others can build monitors for other topics than those chosen in this project.

\end{quote}

