\chapter{\label{cpt:scenarios}Usage scenarios}

\section{A story is posted to a weblog}

When a story is posted on a weblog, it will show up in its RSS feed (this
happens of course outside of our responsibility). If \Amber\ is monitoring this
particular weblog, it will retrieve the story and analyze it. The story is then
displayed on a screen using the results of the analysis.

To get a more concrete idea, suppose \Amber\ is monitoring various A.I. related
weblogs and we would like to find out what they are mainly writing about. We
configure the analysis component in such a way that it can decide whether a
certain subject is dealt with in a story, thereby creating a profile for every
story. Stories with similar subjects will then show up close to eachother in
the display, stories with orthogonal subjects will be very far apart.

The result is an image with various ``clouds'' of in some way related stories.

\section{A discussion is held on a web forum}

Discussions on web forums can get lengthy and the main subject can change
multiple times during their lives. To get an idea what subjects the whole
discussion has been about, \Amber\ can show a cloud map of (part of) the
discussion. It could even show an animation to show how the discussion
developed over time.

Using the animated view of the discussion development, a new participant in the
discussion can decide upon whether bringing up an old discussion point is a
good idea or not. It is also a way to locate a certain subject within a long
list of replies.

