\chapter{\label{cpt:planning}Planning}

The actual internship period amounts to 14 weeks and starts week 34. Before the
actual working period has started, the assignment was already largely agreed
upon.

A week by week planning and logbook was held during the internship at the web
address \url{http://nemendur.ru.is/christian06/logbook.html}.

\section{Weeks 34 and 35: Introduction}

\paragraph{Plan} Learning the organization, people, methodologies and
procedures.

\paragraph{Actions} According to plan, read and talked a lot. Also did
experiments with Psyclone.

\section{Weeks 36 and 37: Global architecture design}

\paragraph{Plan} Having a global design of the modules and a first bit of
object model, meanwhile playing around with posting and retrieving messages
with Psyclone.

\paragraph{Actions} Mainly work on design, also created first version of the
Psyclone specification file. Setting up project in Eclipse, preparing codebase.
Laptop got problems, installed a desktop computer. First simple prototype of
visualizer module (single dot orbiting a circle).

\section{Weeks 38---44: Detailed design and coding}

\paragraph{Plan} Create detailed design and code, starting with basic
visualization, then the crawler module, the analysis module and then the final
visualizer. Each module should at most take two weeks to implement.

\paragraph{Actions} Fully implemented all modules, leaving only a few minor
features which were implemented in week 45 during refactoring.

\section{Week 45: Spare week for coding}

\paragraph{Plan} Refactoring, fixing bugs, completing Javadoc code
documentation.

\paragraph{Actions} Preparing work for internship report document and source
code documentation for the design document.

\section{Weeks 46 and 47: Finishing up}

\paragraph{Plan} Fine-tune crawling, analysis and visualization parameters.
Create final distribution files. Test those on various platforms. No more large
design and source code changes; only bugfixing.

\paragraph{Actions} 

\section{Week 48: Back in Eindhoven}

\paragraph{Plan} Finish internship report and paperworks.

\paragraph{Actions} 

