\documentclass[english,a4paper,twoside]{scrreprt}

\usepackage{design}

\acrodef{RU}{Reykjavík University}
\acrodef{CADIA}{Center for Analysis \& Design of Intelligent Agents}
\acrodef{RSS}{Rich Site Summary}
\acrodef{YAML}{YAML Ain't Markup Language}
\acrodef{OPML}{Outline Processor Markup Language}

% Document meta data.
%FIXME: better title & remove draft suffix
\title{Ambient Earth\\
       {\Large \emph{Design Document --- 1$^{\text{st}}$ draft\/}}}
\author{Christian Luijten\\\url{christian06@ru.is}}
\date{\today}
\institution{
 Center for Analysis and Design of Intelligent Agents \\
 School of Science and Engineering \\
 Reykjavík University, Reykjavík \\[1em]
 \emph{Under supervision of:\/} \\
 Kristinn R. Thórisson, Ph.D. (Reykjavík University) \\
 dr.ir. Huub van de Wetering (Eindhoven University of Technology) \\
}

\begin{document}

\maketitle

\begin{abstract}
  This document describes the design of the Ambient Earth system. Ambient Earth
  is a software system for visualization of Internet activity.
\end{abstract}

\vfill

\begin{adjustwidth}{4em}{4em}
{\scriptsize
  Christian Luijten (\url{christian06@ru.is})

  Copyright \copyright\ 2006 Center for Analysis and Design of Intelligent
  Agents. \\
  Reykjavík University \\
  All rights reserved

  \url{http://cadia.ru.is/}

  Redistribution and use in source and binary forms, with or without
  modification, is permitted provided that the following conditions are met:

  \begin{itemize}
    \item Redistributions of source code must retain the above copyright
      notice, this list of conditions and the following disclaimer.

    \item Redistributions in binary form must reproduce the above copyright
      notice, this list of conditions and the following disclaimer in the
      documentation and/or other materials provided with the distribution.

    \item Neither the name of its copyright holders nor the names of its
      contributors may be used to endorse or promote products derived from this
      software without specific prior written permission.

  \end{itemize}

  THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
  AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
  IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
  ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE
  LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
  CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
  SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
  INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
  CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
  ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
  POSSIBILITY OF SUCH DAMAGE.

  % The contents of this and the following documents and the \LaTeX\ source
  % code that is used to generate them is licensed under the Creative Commons
  % Attribution-ShareAlike 2.5 license. 

  % You are free:
  % \begin{itemize}
    % \item to copy, distribute, display, and perform the work
    % \item to make derivative works
    % \item to make commercial use of the work
  % \end{itemize}

  % Under the following conditions:
  % \begin{description}
    % \item[Attribution:] You must attribute the work in the manner specified by
      % the author or licensor.
    % \item[Share Alike:] If you alter, transform, or build upon this work, you
      % may distribute the resulting work only under a license identical to this
      % one.
  % \end{description}

  % \begin{itemize}
    % \item For any reuse or distribution, you must make clear to others the
      % license terms of this work.
    % \item Any of these conditions can be waived if you get permission from
      % the copyright holder.
  % \end{itemize}

  % Your fair use and other rights are in no way affected by the above.

  % This is a human-readable summary of the Legal Code, for the full license
  % please refer to:
  % \mbox{\url{http://creativecommons.org/licenses/by-sa/2.5/legalcode}}.

}
\end{adjustwidth}

\newpage

\tableofcontents

\include{\designpath/01-intro.inc}

\include{\designpath/02-scenarios.inc}

\include{\designpath/03-requirements.inc}

\include{\designpath/04-architecture.inc}

\include{\designpath/05-detailed.inc}

% \include{\designpath/06-conclusion.inc}

% \appendix

% \chapter{Auto-generated javadoc source code documentation}
% \include{\designpath/design-appendix-javadoc.inc}

\bibliographystyle{cadia}
\bibliography{bibliography}
\addcontentsline{toc}{chapter}{\refname}

\end{document}
